SI

### 2021-01-06 ms/manuscript.Rmd
Use bare variable names for tar_load
or dependencies won't get tracked
https://github.com/wlandau/tarchetypes/issues/26

```{r load-data}
tar_load(
  names = c(
    "refs",
    "refs_other",
    "climate",
    "filmy_species",
    "moorea_sites",
    "phylosig",
    "range_types",
    "combined_species_means",
    "t_test_results",
    "env_range_dt_model_summary"
  )
)
```

>>>>

```{r load-data}
tar_load(refs)
tar_load(refs_other)
tar_load(climate)
tar_load(filmy_species)
tar_load(moorea_sites)
tar_load(phylosig)
tar_load(range_types)
tar_load(combined_species_means)
tar_load(t_test_results)
tar_load(env_range_dt_model_summary)
tar_load(recovery_species_means)
tar_load(filmy_habit)
```

### 2021-01-06 ms/si.Rmd
Use bare variable names for tar_load
or dependencies won't get tracked
https://github.com/wlandau/tarchetypes/issues/26

```{r load-data, cache = FALSE}
tar_load(
  names = c(
    "filmy_dt_chamber",
    "filmy_dt",
    "filmy_habit",
    "rel_water_indiv",
    "rel_water_species_means"
  )
)
```

>>>>

```{r load-data, cache = FALSE}
tar_load(filmy_dt_chamber)
tar_load(filmy_dt)
tar_load(filmy_habit)
tar_load(rel_water_indiv)
tar_load(rel_water_species_means)
```
